### 2019-06-14 2-Chapters/3-Chapter/chapter3.tex
Starting to add the new figures

\begin{enumerate}
    \item
    %  Algorithm 1 is
    $\varepsilon$-greedy \cite{Bubeck12} (\texttt{EpsilonDecreasing}), shown in Algorithm~\ref{algo:2:naiveStrategies} above, using $\varepsilon_t = \varepsilon_0 / t$, and $\varepsilon_0 = 0.1$ (chosen arbitrarily).
    It has a very small cost in terms of time and memory, but it usually achieves linear regret.

    \item
    %  Algorithm 2 is
    Explore-then-Commit \cite{GarivierETC2016} (\texttt{ETC\_KnownGap}), shown in Algorithm~\ref{algo:2:naiveStrategies} above, that knows the horizon, and a lower-bound on the gap between arms (chosen arbitrarily as $\delta=0.01$, valid for all problems).
    Similarly to $\varepsilon$-greedy, it has a very small footprint in terms of time and memory, but most of the times it only obtains large (linear) regret.

@@

    \item
    %  Algorithm 5 is
    \klUCB{} from \cite{KLUCBJournal} (\texttt{klUCB}), also shown in Algorithm~\ref{algo:2:indexPolicy} above, using the Bernoulli KL divergence and the corresponding \klUCB{} indexes, implemented as \texttt{kullback.klucbBern}.
    % It achieves asymptotical optimal problem-dependent bounds with a $\cO(\log(T))$ regret.
    % with the scaling factor matching Lai and Robbins' lower-bound \cite{LaiRobbins85}.
    It is computationally more costly that \UCB, as at each time step $t$ and for each arm $k$, a convex optimization problem must be solved approximately, in order to compute the $K$ indexes.
    In practice, a few steps of a simple bisection search method are enough to obtain a good numerical precision, and empirically we found that even in the worst cases \klUCB{} is no more than one order of magnitude slower than \UCB.
    % of more than 10 digits
    % \TODOL{Si on en pas parlé avant, ou après dans une annexe, je peux dire un mot ici à propos de l'implémentation en Cython ou en C des fonctions kl et indices kl-UCB !}

@@

%         $\varepsilon$-greedy &
%             $R^{1}_{T_1,K_1} = 0 \pm 0$
%                 $R^{1}_{T_1,K_2} = 0 \pm 0$
%                 $R^{1}_{T_1,K_3} = 0 \pm 0$
%                 $R^{1}_{T_1,K_4} = 0 \pm 0$
%                 $R^{1}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{1}_{T_2,K_1} = 0 \pm 0$
%                 $R^{1}_{T_2,K_2} = 0 \pm 0$
%                 $R^{1}_{T_2,K_3} = 0 \pm 0$
%                 $R^{1}_{T_2,K_4} = 0 \pm 0$
%                 $R^{1}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{1}_{T_3,K_1} = 0 \pm 0$
%                 $R^{1}_{T_3,K_2} = 0 \pm 0$
%                 $R^{1}_{T_3,K_3} = 0 \pm 0$
%                 $R^{1}_{T_3,K_4} = 0 \pm 0$
%                 $R^{1}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{1}_{T_4,K_1} = 0 \pm 0$
%                 $R^{1}_{T_4,K_2} = 0 \pm 0$
%                 $R^{1}_{T_4,K_3} = 0 \pm 0$
%                 $R^{1}_{T_4,K_4} = 0 \pm 0$
%                 $R^{1}_{T_4,K_5} = 0 \pm 0$ \\
%         Explore-then-Commit &
%             $R^{2}_{T_1,K_1} = 0 \pm 0$
%                 $R^{2}_{T_1,K_2} = 0 \pm 0$
%                 $R^{2}_{T_1,K_3} = 0 \pm 0$
%                 $R^{2}_{T_1,K_4} = 0 \pm 0$
%                 $R^{2}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{2}_{T_2,K_1} = 0 \pm 0$
%                 $R^{2}_{T_2,K_2} = 0 \pm 0$
%                 $R^{2}_{T_2,K_3} = 0 \pm 0$
%                 $R^{2}_{T_2,K_4} = 0 \pm 0$
%                 $R^{2}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{2}_{T_3,K_1} = 0 \pm 0$
%                 $R^{2}_{T_3,K_2} = 0 \pm 0$
%                 $R^{2}_{T_3,K_3} = 0 \pm 0$
%                 $R^{2}_{T_3,K_4} = 0 \pm 0$
%                 $R^{2}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{2}_{T_4,K_1} = 0 \pm 0$
%                 $R^{2}_{T_4,K_2} = 0 \pm 0$
%                 $R^{2}_{T_4,K_3} = 0 \pm 0$
%                 $R^{2}_{T_4,K_4} = 0 \pm 0$
%                 $R^{2}_{T_4,K_5} = 0 \pm 0$ \\
%         $\mathrm{Exp}3^{++}$ &
%             $R^3_{T_1,K_1} = 0 \pm 0$
%                 $R^3_{T_1,K_2} = 0 \pm 0$
%                 $R^3_{T_1,K_3} = 0 \pm 0$
%                 $R^3_{T_1,K_4} = 0 \pm 0$
%                 $R^3_{T_1,K_5} = 0 \pm 0$ &
%             $R^3_{T_2,K_1} = 0 \pm 0$
%                 $R^3_{T_2,K_2} = 0 \pm 0$
%                 $R^3_{T_2,K_3} = 0 \pm 0$
%                 $R^3_{T_2,K_4} = 0 \pm 0$
%                 $R^3_{T_2,K_5} = 0 \pm 0$ &
%             $R^3_{T_3,K_1} = 0 \pm 0$
%                 $R^3_{T_3,K_2} = 0 \pm 0$
%                 $R^3_{T_3,K_3} = 0 \pm 0$
%                 $R^3_{T_3,K_4} = 0 \pm 0$
%                 $R^3_{T_3,K_5} = 0 \pm 0$ &
%             $R^3_{T_4,K_1} = 0 \pm 0$
%                 $R^3_{T_4,K_2} = 0 \pm 0$
%                 $R^3_{T_4,K_3} = 0 \pm 0$
%                 $R^3_{T_4,K_4} = 0 \pm 0$
%                 $R^3_{T_4,K_5} = 0 \pm 0$ \\
%         $\UCB_1$ &
%             $R^{4}_{T_1,K_1} = 0 \pm 0$
%                 $R^{4}_{T_1,K_2} = 0 \pm 0$
%                 $R^{4}_{T_1,K_3} = 0 \pm 0$
%                 $R^{4}_{T_1,K_4} = 0 \pm 0$
%                 $R^{4}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{4}_{T_2,K_1} = 0 \pm 0$
%                 $R^{4}_{T_2,K_2} = 0 \pm 0$
%                 $R^{4}_{T_2,K_3} = 0 \pm 0$
%                 $R^{4}_{T_2,K_4} = 0 \pm 0$
%                 $R^{4}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{4}_{T_3,K_1} = 0 \pm 0$
%                 $R^{4}_{T_3,K_2} = 0 \pm 0$
%                 $R^{4}_{T_3,K_3} = 0 \pm 0$
%                 $R^{4}_{T_3,K_4} = 0 \pm 0$
%                 $R^{4}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{4}_{T_4,K_1} = 0 \pm 0$
%                 $R^{4}_{T_4,K_2} = 0 \pm 0$
%                 $R^{4}_{T_4,K_3} = 0 \pm 0$
%                 $R^{4}_{T_4,K_4} = 0 \pm 0$
%                 $R^{4}_{T_4,K_5} = 0 \pm 0$ \\
%         \klUCB{} &
%             $R^{5}_{T_1,K_1} = 0 \pm 0$
%                 $R^{5}_{T_1,K_2} = 0 \pm 0$
%                 $R^{5}_{T_1,K_3} = 0 \pm 0$
%                 $R^{5}_{T_1,K_4} = 0 \pm 0$
%                 $R^{5}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{5}_{T_2,K_1} = 0 \pm 0$
%                 $R^{5}_{T_2,K_2} = 0 \pm 0$
%                 $R^{5}_{T_2,K_3} = 0 \pm 0$
%                 $R^{5}_{T_2,K_4} = 0 \pm 0$
%                 $R^{5}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{5}_{T_3,K_1} = 0 \pm 0$
%                 $R^{5}_{T_3,K_2} = 0 \pm 0$
%                 $R^{5}_{T_3,K_3} = 0 \pm 0$
%                 $R^{5}_{T_3,K_4} = 0 \pm 0$
%                 $R^{5}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{5}_{T_4,K_1} = 0 \pm 0$
%                 $R^{5}_{T_4,K_2} = 0 \pm 0$
%                 $R^{5}_{T_4,K_3} = 0 \pm 0$
%                 $R^{5}_{T_4,K_4} = 0 \pm 0$
%                 $R^{5}_{T_4,K_5} = 0 \pm 0$ \\
%         Thompson sampling &
%             $R^{6}_{T_1,K_1} = 0 \pm 0$
%                 $R^{6}_{T_1,K_2} = 0 \pm 0$
%                 $R^{6}_{T_1,K_3} = 0 \pm 0$
%                 $R^{6}_{T_1,K_4} = 0 \pm 0$
%                 $R^{6}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{6}_{T_2,K_1} = 0 \pm 0$
%                 $R^{6}_{T_2,K_2} = 0 \pm 0$
%                 $R^{6}_{T_2,K_3} = 0 \pm 0$
%                 $R^{6}_{T_2,K_4} = 0 \pm 0$
%                 $R^{6}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{6}_{T_3,K_1} = 0 \pm 0$
%                 $R^{6}_{T_3,K_2} = 0 \pm 0$
%                 $R^{6}_{T_3,K_3} = 0 \pm 0$
%                 $R^{6}_{T_3,K_4} = 0 \pm 0$
%                 $R^{6}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{6}_{T_4,K_1} = 0 \pm 0$
%                 $R^{6}_{T_4,K_2} = 0 \pm 0$
%                 $R^{6}_{T_4,K_3} = 0 \pm 0$
%                 $R^{6}_{T_4,K_4} = 0 \pm 0$
%                 $R^{6}_{T_4,K_5} = 0 \pm 0$ \\
%         Thompson sampling &
%             $R^{7}_{T_1,K_1} = 0 \pm 0$
%                 $R^{7}_{T_1,K_2} = 0 \pm 0$
%                 $R^{7}_{T_1,K_3} = 0 \pm 0$
%                 $R^{7}_{T_1,K_4} = 0 \pm 0$
%                 $R^{7}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{7}_{T_2,K_1} = 0 \pm 0$
%                 $R^{7}_{T_2,K_2} = 0 \pm 0$
%                 $R^{7}_{T_2,K_3} = 0 \pm 0$
%                 $R^{7}_{T_2,K_4} = 0 \pm 0$
%                 $R^{7}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{7}_{T_3,K_1} = 0 \pm 0$
%                 $R^{7}_{T_3,K_2} = 0 \pm 0$
%                 $R^{7}_{T_3,K_3} = 0 \pm 0$
%                 $R^{7}_{T_3,K_4} = 0 \pm 0$
%                 $R^{7}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{7}_{T_4,K_1} = 0 \pm 0$
%                 $R^{7}_{T_4,K_2} = 0 \pm 0$
%                 $R^{7}_{T_4,K_3} = 0 \pm 0$
%                 $R^{7}_{T_4,K_4} = 0 \pm 0$
%                 $R^{7}_{T_4,K_5} = 0 \pm 0$ \\
%         AdBandits &
%             $R^{8}_{T_1,K_1} = 0 \pm 0$
%                 $R^{8}_{T_1,K_2} = 0 \pm 0$
%                 $R^{8}_{T_1,K_3} = 0 \pm 0$
%                 $R^{8}_{T_1,K_4} = 0 \pm 0$
%                 $R^{8}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{8}_{T_2,K_1} = 0 \pm 0$
%                 $R^{8}_{T_2,K_2} = 0 \pm 0$
%                 $R^{8}_{T_2,K_3} = 0 \pm 0$
%                 $R^{8}_{T_2,K_4} = 0 \pm 0$
%                 $R^{8}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{8}_{T_3,K_1} = 0 \pm 0$
%                 $R^{8}_{T_3,K_2} = 0 \pm 0$
%                 $R^{8}_{T_3,K_3} = 0 \pm 0$
%                 $R^{8}_{T_3,K_4} = 0 \pm 0$
%                 $R^{8}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{8}_{T_4,K_1} = 0 \pm 0$
%                 $R^{8}_{T_4,K_2} = 0 \pm 0$
%                 $R^{8}_{T_4,K_3} = 0 \pm 0$
%                 $R^{8}_{T_4,K_4} = 0 \pm 0$
%                 $R^{8}_{T_4,K_5} = 0 \pm 0$ \\
%         BESA &
%             $R^{9}_{T_1,K_1} = 0 \pm 0$
%                 $R^{9}_{T_1,K_2} = 0 \pm 0$
%                 $R^{9}_{T_1,K_3} = 0 \pm 0$
%                 $R^{9}_{T_1,K_4} = 0 \pm 0$
%                 $R^{9}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{9}_{T_2,K_1} = 0 \pm 0$
%                 $R^{9}_{T_2,K_2} = 0 \pm 0$
%                 $R^{9}_{T_2,K_3} = 0 \pm 0$
%                 $R^{9}_{T_2,K_4} = 0 \pm 0$
%                 $R^{9}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{9}_{T_3,K_1} = 0 \pm 0$
%                 $R^{9}_{T_3,K_2} = 0 \pm 0$
%                 $R^{9}_{T_3,K_3} = 0 \pm 0$
%                 $R^{9}_{T_3,K_4} = 0 \pm 0$
%                 $R^{9}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{9}_{T_4,K_1} = 0 \pm 0$
%                 $R^{9}_{T_4,K_2} = 0 \pm 0$
%                 $R^{9}_{T_4,K_3} = 0 \pm 0$
%                 $R^{9}_{T_4,K_4} = 0 \pm 0$
%                 $R^{9}_{T_4,K_5} = 0 \pm 0$ \\
%     \caption{Mean regret $\pm$ $1$ std-dev, for $9$ different algorithms on \textbf{problem 1} with different values of time $T$ and number of arm $K$.
%     \label{table:3:meanRegret_problem1}
%         $\varepsilon$-greedy &
%             $R^{'1}_{T_1,K_1} = 0 \pm 0$
%                 $R^{'1}_{T_1,K_2} = 0 \pm 0$
%                 $R^{'1}_{T_1,K_3} = 0 \pm 0$
%                 $R^{'1}_{T_1,K_4} = 0 \pm 0$
%                 $R^{'1}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{'1}_{T_2,K_1} = 0 \pm 0$
%                 $R^{'1}_{T_2,K_2} = 0 \pm 0$
%                 $R^{'1}_{T_2,K_3} = 0 \pm 0$
%                 $R^{'1}_{T_2,K_4} = 0 \pm 0$
%                 $R^{'1}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{'1}_{T_3,K_1} = 0 \pm 0$
%                 $R^{'1}_{T_3,K_2} = 0 \pm 0$
%                 $R^{'1}_{T_3,K_3} = 0 \pm 0$
%                 $R^{'1}_{T_3,K_4} = 0 \pm 0$
%                 $R^{'1}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{'1}_{T_4,K_1} = 0 \pm 0$
%                 $R^{'1}_{T_4,K_2} = 0 \pm 0$
%                 $R^{'1}_{T_4,K_3} = 0 \pm 0$
%                 $R^{'1}_{T_4,K_4} = 0 \pm 0$
%                 $R^{'1}_{T_4,K_5} = 0 \pm 0$ \\
%         Explore-then-Commit &
%             $R^{'2}_{T_1,K_1} = 0 \pm 0$
%                 $R^{'2}_{T_1,K_2} = 0 \pm 0$
%                 $R^{'2}_{T_1,K_3} = 0 \pm 0$
%                 $R^{'2}_{T_1,K_4} = 0 \pm 0$
%                 $R^{'2}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{'2}_{T_2,K_1} = 0 \pm 0$
%                 $R^{'2}_{T_2,K_2} = 0 \pm 0$
%                 $R^{'2}_{T_2,K_3} = 0 \pm 0$
%                 $R^{'2}_{T_2,K_4} = 0 \pm 0$
%                 $R^{'2}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{'2}_{T_3,K_1} = 0 \pm 0$
%                 $R^{'2}_{T_3,K_2} = 0 \pm 0$
%                 $R^{'2}_{T_3,K_3} = 0 \pm 0$
%                 $R^{'2}_{T_3,K_4} = 0 \pm 0$
%                 $R^{'2}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{'2}_{T_4,K_1} = 0 \pm 0$
%                 $R^{'2}_{T_4,K_2} = 0 \pm 0$
%                 $R^{'2}_{T_4,K_3} = 0 \pm 0$
%                 $R^{'2}_{T_4,K_4} = 0 \pm 0$
%                 $R^{'2}_{T_4,K_5} = 0 \pm 0$ \\
%         $\mathrm{Exp}3^{++}$ &
%             $R^{'3}_{T_1,K_1} = 0 \pm 0$
%                 $R^{'3}_{T_1,K_2} = 0 \pm 0$
%                 $R^{'3}_{T_1,K_3} = 0 \pm 0$
%                 $R^{'3}_{T_1,K_4} = 0 \pm 0$
%                 $R^{'3}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{'3}_{T_2,K_1} = 0 \pm 0$
%                 $R^{'3}_{T_2,K_2} = 0 \pm 0$
%                 $R^{'3}_{T_2,K_3} = 0 \pm 0$
%                 $R^{'3}_{T_2,K_4} = 0 \pm 0$
%                 $R^{'3}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{'3}_{T_3,K_1} = 0 \pm 0$
%                 $R^{'3}_{T_3,K_2} = 0 \pm 0$
%                 $R^{'3}_{T_3,K_3} = 0 \pm 0$
%                 $R^{'3}_{T_3,K_4} = 0 \pm 0$
%                 $R^{'3}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{'3}_{T_4,K_1} = 0 \pm 0$
%                 $R^{'3}_{T_4,K_2} = 0 \pm 0$
%                 $R^{'3}_{T_4,K_3} = 0 \pm 0$
%                 $R^{'3}_{T_4,K_4} = 0 \pm 0$
%                 $R^{'3}_{T_4,K_5} = 0 \pm 0$ \\
%         $\UCB_1$ &
%             $R^{'4}_{T_1,K_1} = 0 \pm 0$
%                 $R^{'4}_{T_1,K_2} = 0 \pm 0$
%                 $R^{'4}_{T_1,K_3} = 0 \pm 0$
%                 $R^{'4}_{T_1,K_4} = 0 \pm 0$
%                 $R^{'4}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{'4}_{T_2,K_1} = 0 \pm 0$
%                 $R^{'4}_{T_2,K_2} = 0 \pm 0$
%                 $R^{'4}_{T_2,K_3} = 0 \pm 0$
%                 $R^{'4}_{T_2,K_4} = 0 \pm 0$
%                 $R^{'4}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{'4}_{T_3,K_1} = 0 \pm 0$
%                 $R^{'4}_{T_3,K_2} = 0 \pm 0$
%                 $R^{'4}_{T_3,K_3} = 0 \pm 0$
%                 $R^{'4}_{T_3,K_4} = 0 \pm 0$
%                 $R^{'4}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{'4}_{T_4,K_1} = 0 \pm 0$
%                 $R^{'4}_{T_4,K_2} = 0 \pm 0$
%                 $R^{'4}_{T_4,K_3} = 0 \pm 0$
%                 $R^{'4}_{T_4,K_4} = 0 \pm 0$
%                 $R^{'4}_{T_4,K_5} = 0 \pm 0$ \\
%         \klUCB{} &
%             $R^{'5}_{T_1,K_1} = 0 \pm 0$
%                 $R^{'5}_{T_1,K_2} = 0 \pm 0$
%                 $R^{'5}_{T_1,K_3} = 0 \pm 0$
%                 $R^{'5}_{T_1,K_4} = 0 \pm 0$
%                 $R^{'5}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{'5}_{T_2,K_1} = 0 \pm 0$
%                 $R^{'5}_{T_2,K_2} = 0 \pm 0$
%                 $R^{'5}_{T_2,K_3} = 0 \pm 0$
%                 $R^{'5}_{T_2,K_4} = 0 \pm 0$
%                 $R^{'5}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{'5}_{T_3,K_1} = 0 \pm 0$
%                 $R^{'5}_{T_3,K_2} = 0 \pm 0$
%                 $R^{'5}_{T_3,K_3} = 0 \pm 0$
%                 $R^{'5}_{T_3,K_4} = 0 \pm 0$
%                 $R^{'5}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{'5}_{T_4,K_1} = 0 \pm 0$
%                 $R^{'5}_{T_4,K_2} = 0 \pm 0$
%                 $R^{'5}_{T_4,K_3} = 0 \pm 0$
%                 $R^{'5}_{T_4,K_4} = 0 \pm 0$
%                 $R^{'5}_{T_4,K_5} = 0 \pm 0$ \\
%         Thompson sampling &
%             $R^{'6}_{T_1,K_1} = 0 \pm 0$
%                 $R^{'6}_{T_1,K_2} = 0 \pm 0$
%                 $R^{'6}_{T_1,K_3} = 0 \pm 0$
%                 $R^{'6}_{T_1,K_4} = 0 \pm 0$
%                 $R^{'6}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{'6}_{T_2,K_1} = 0 \pm 0$
%                 $R^{'6}_{T_2,K_2} = 0 \pm 0$
%                 $R^{'6}_{T_2,K_3} = 0 \pm 0$
%                 $R^{'6}_{T_2,K_4} = 0 \pm 0$
%                 $R^{'6}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{'6}_{T_3,K_1} = 0 \pm 0$
%                 $R^{'6}_{T_3,K_2} = 0 \pm 0$
%                 $R^{'6}_{T_3,K_3} = 0 \pm 0$
%                 $R^{'6}_{T_3,K_4} = 0 \pm 0$
%                 $R^{'6}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{'6}_{T_4,K_1} = 0 \pm 0$
%                 $R^{'6}_{T_4,K_2} = 0 \pm 0$
%                 $R^{'6}_{T_4,K_3} = 0 \pm 0$
%                 $R^{'6}_{T_4,K_4} = 0 \pm 0$
%                 $R^{'6}_{T_4,K_5} = 0 \pm 0$ \\
%         Bayes-UCB &
%             $R^{'7}_{T_1,K_1} = 0 \pm 0$
%                 $R^{'7}_{T_1,K_2} = 0 \pm 0$
%                 $R^{'7}_{T_1,K_3} = 0 \pm 0$
%                 $R^{'7}_{T_1,K_4} = 0 \pm 0$
%                 $R^{'7}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{'7}_{T_2,K_1} = 0 \pm 0$
%                 $R^{'7}_{T_2,K_2} = 0 \pm 0$
%                 $R^{'7}_{T_2,K_3} = 0 \pm 0$
%                 $R^{'7}_{T_2,K_4} = 0 \pm 0$
%                 $R^{'7}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{'7}_{T_3,K_1} = 0 \pm 0$
%                 $R^{'7}_{T_3,K_2} = 0 \pm 0$
%                 $R^{'7}_{T_3,K_3} = 0 \pm 0$
%                 $R^{'7}_{T_3,K_4} = 0 \pm 0$
%                 $R^{'7}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{'7}_{T_4,K_1} = 0 \pm 0$
%                 $R^{'7}_{T_4,K_2} = 0 \pm 0$
%                 $R^{'7}_{T_4,K_3} = 0 \pm 0$
%                 $R^{'7}_{T_4,K_4} = 0 \pm 0$
%                 $R^{'7}_{T_4,K_5} = 0 \pm 0$ \\
%         AdBandits &
%             $R^{'8}_{T_1,K_1} = 0 \pm 0$
%                 $R^{'8}_{T_1,K_2} = 0 \pm 0$
%                 $R^{'8}_{T_1,K_3} = 0 \pm 0$
%                 $R^{'8}_{T_1,K_4} = 0 \pm 0$
%                 $R^{'8}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{'8}_{T_2,K_1} = 0 \pm 0$
%                 $R^{'8}_{T_2,K_2} = 0 \pm 0$
%                 $R^{'8}_{T_2,K_3} = 0 \pm 0$
%                 $R^{'8}_{T_2,K_4} = 0 \pm 0$
%                 $R^{'8}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{'8}_{T_3,K_1} = 0 \pm 0$
%                 $R^{'8}_{T_3,K_2} = 0 \pm 0$
%                 $R^{'8}_{T_3,K_3} = 0 \pm 0$
%                 $R^{'8}_{T_3,K_4} = 0 \pm 0$
%                 $R^{'8}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{'8}_{T_4,K_1} = 0 \pm 0$
%                 $R^{'8}_{T_4,K_2} = 0 \pm 0$
%                 $R^{'8}_{T_4,K_3} = 0 \pm 0$
%                 $R^{'8}_{T_4,K_4} = 0 \pm 0$
%                 $R^{'8}_{T_4,K_5} = 0 \pm 0$ \\
%         BESA &
%             $R^{'9}_{T_1,K_1} = 0 \pm 0$
%                 $R^{'9}_{T_1,K_2} = 0 \pm 0$
%                 $R^{'9}_{T_1,K_3} = 0 \pm 0$
%                 $R^{'9}_{T_1,K_4} = 0 \pm 0$
%                 $R^{'9}_{T_1,K_5} = 0 \pm 0$ &
%             $R^{'9}_{T_2,K_1} = 0 \pm 0$
%                 $R^{'9}_{T_2,K_2} = 0 \pm 0$
%                 $R^{'9}_{T_2,K_3} = 0 \pm 0$
%                 $R^{'9}_{T_2,K_4} = 0 \pm 0$
%                 $R^{'9}_{T_2,K_5} = 0 \pm 0$ &
%             $R^{'9}_{T_3,K_1} = 0 \pm 0$
%                 $R^{'9}_{T_3,K_2} = 0 \pm 0$
%                 $R^{'9}_{T_3,K_3} = 0 \pm 0$
%                 $R^{'9}_{T_3,K_4} = 0 \pm 0$
%                 $R^{'9}_{T_3,K_5} = 0 \pm 0$ &
%             $R^{'9}_{T_4,K_1} = 0 \pm 0$
%                 $R^{'9}_{T_4,K_2} = 0 \pm 0$
%                 $R^{'9}_{T_4,K_3} = 0 \pm 0$
%                 $R^{'9}_{T_4,K_4} = 0 \pm 0$
%                 $R^{'9}_{T_4,K_5} = 0 \pm 0$ \\
%     \caption{Mean regret $\pm$ $1$ std-dev, for $9$ different algorithms on \textbf{problem 2} with different values of time $T$ and number of arm $K$.
%     \label{table:3:meanRegret_problem2}

% Include in appendix of this chapter the results for 7 more algorithms, the most recent and less important ones (MOSSAnytime, ApproximatedFHGittins, UCBdagger, klUCBswitchAnytime, PHE, RCB, Tsallis-Inf)

% FIXME generate from the notebook then copy from WS3
\begin{figure}[h!]  % [htbp]
	% \centering
	\includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormregret_vs_arms__56pb__7Ks_T50000.pdf}
	\caption[Regret vs different values of $K$.]{
        Regret vs different values of $K$ ($R_T / \log(T)$),
        for $T=50000$ and for $16$ algorithms.
        The $y$-axis is in log-scale.
        All algorithms appear to have a regret slowly growing with respect to $K$, as predicted by the regret bounds which are linear with respect to the number of arms, as predicted.
        \textsc{Tsallis-Inf} is the only state-of-the-art algorithm which appears to be very inefficient for problems with a small number of arms.
        Both the $\varepsilon$-greedy and Explore-then-Commit algorithms performed poorly, achieving linear regret (not displayed).
	}
	\label{fig:3:16_different_algorithms__lognormregret_vs_arms__56pb__7Ks_T50000}
\end{figure}

>>>>

\begin{enumerate}
    \item
    %  Algorithm 1 is
    $\varepsilon$-greedy \cite{Bubeck12} (\texttt{EpsilonDecreasing}),
    % shown in Algorithm~\ref{algo:2:naiveStrategies} above,
    using $\varepsilon_t = \varepsilon_0 / t$, and $\varepsilon_0 = 0.1$ (chosen arbitrarily).
    It has a very small cost in terms of time and memory, but it usually achieves linear regret.

    \item
    %  Algorithm 2 is
    Explore-then-Commit \cite{GarivierETC2016} (\texttt{ETC\_KnownGap}),
    % shown in Algorithm~\ref{algo:2:naiveStrategies} above,
    that knows the horizon, and a lower-bound on the gap between arms (chosen arbitrarily as $\delta=0.01$, valid for all problems).
    Similarly to $\varepsilon$-greedy, it has a very small footprint in terms of time and memory, but most of the times it only obtains large (linear) regret.

@@

    \item
    %  Algorithm 5 is
    \klUCB{} from \cite{KLUCBJournal} (\texttt{klUCB}), also shown in Algorithm~\ref{algo:2:indexPolicy} above, using the Bernoulli KL divergence and the corresponding \klUCB{} indexes (coded as \texttt{kullback.klucbBern}).
    % It achieves asymptotical optimal problem-dependent bounds with a $\cO(\log(T))$ regret.
    % with the scaling factor matching Lai and Robbins' lower-bound \cite{LaiRobbins85}.
    It is computationally more costly that \UCB, as at each time step $t$ and for each arm $k$, a convex optimization problem must be solved approximately, in order to compute the $K$ indexes.
    In practice, a few steps of a simple bisection search method are enough to obtain a good numerical precision, and empirically we found that even in the worst cases \klUCB{} is no more than one order of magnitude slower than \UCB.
    % of more than 10 digits
    % \TODOL{Si on en pas parlé avant, ou après dans une annexe, je peux dire un mot ici à propos de l'implémentation en Cython ou en C des fonctions kl et indices kl-UCB !}

@@

\begin{figure}[h!]  % [htbp]
	% \centering
	% \includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormregret_vs_arms__56pb__7Ks_T50000.pdf}
	\includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormregret_vs_arms__16pb__T5000.pdf}
	\caption[Regret vs different values of $K$.]{
        Regret vs different values of $K$ ($R_T / \log(T)$),
        for $T=5000$ and for $16$ algorithms.
        The $y$-axis is in log-scale.
        All algorithms appear to have a regret slowly growing with respect to $K$, as predicted by the regret bounds which are linear with respect to the number of arms, as predicted.
        \textsc{Tsallis-Inf} is the only state-of-the-art algorithm which appears to be very inefficient for problems with a small number of arms.
        Both the $\varepsilon$-greedy and Explore-then-Commit algorithms performed poorly, achieving linear regret (not displayed).
	}
	\label{fig:3:16_different_algorithms__lognormregret_vs_arms__16pb__T5000}
\end{figure}

\begin{figure}[h!]  % [htbp]
	% \centering
	% \includegraphics[width=1.10\linewidth]{16_different_algorithms__normregret_vs_horizons__56pb__K32_7Ts.pdf}
	\includegraphics[width=1.10\linewidth]{16_different_algorithms__lognormregret_vs_times__16pb__K8.pdf}
	\caption[Regret vs different values of $T$.]{
        Regret vs different values of $T$ ($R_T / K$),
        for $K=32$ and for $16$ algorithms.
        All efficient algorithms appear to have a logarithmic regret, meaning that their regret bound is indeed logarithmic with respect to the horizon, as predicted.
        The respective ranking of all the algorithms also appears to remain preserved for different values of $T$, which is also backed-up by theoretical results: if two algorithms $\cA$ and $\cA'$ has a regret close to their regret bounds, of the form $R_T \leq \cO(K \log(T))$, and the bound for $\cA$ use a smaller constant than the bound for $\cA'$, $\cA$ should obtain a smaller regret than $\cA'$ no matter the horizon.
        Finally, we also observe once more than both the $\varepsilon$-greedy and Explore-then-Commit algorithms performed poorly, achieving linear regret (not displayed after $T=100000$).
	}
	\label{fig:3:16_different_algorithms__lognormregret_vs_times__16pb__K8}
\end{figure}

\paragraph{Summary of the experiments.}
%
In the two Figures~\ref{fig:3:16_different_algorithms__lognormregret_vs_arms__16pb__T5000} and \ref{fig:3:16_different_algorithms__lognormregret_vs_times__16pb__K8}
included in this section,
we are able to check empirically that the regret of all the efficient algorithm indeed scales as predicted by the theory, that is
linearly in the number of arms, and logarithmically in the horizon, \ie, $R_T = \bigO{K \log T}$.
%
The main take-away message is the following: in all the rest of this thesis, we focus on two algorithms depending if simplicity or efficiency is favored:
\begin{itemize}\tightlist
    \item
    \UCB{} (or Thompson sampling) is used in the more applied Chapter~\ref{chapter:4}, when simplicity is favored,
    \item
    \klUCB{} is used, in the two more theoretical Chapters~\ref{chapter:5} and \ref{chapter:6}, when efficiency is favored, and when we analyze mathematically the performance of an algorithm that is running on top of a classical stationary MAB policy, like our two contributions, \MCTopM{} and \GLR.
\end{itemize}
